The Effect of Racial and Ethnic Attitudes on Asian Identity in the U.S

### 2024-09-30 my_paper/manuscript_main.tex
edit Hadah forthcoming paper

This paper is most closely related to \textcite{hadahforthcominghispanicidentity, antmanEthnicAttritionObserved2016,antmanIncentivesIdentifyRacial2015,antmanAmericanIndianCasinos2021} where the authors studied the ethnic attrition of Hispanic immigrants and how minorities change their self-reported identity to changes in policies.\footnote{Ethnic attrition is when a person with Asian ancestry fails to self-identify as Asian.} Taking into consideration the ethnic attrition that \textcite{antmanEthnicAttritionObserved2016} document, I investigate the determinants of what drives a person to self-report, or not, their Asian identity. \textcite{hadahforthcominghispanicidentity} finds that bias and self-reported Hispanic identity are negatively associates among a sample of objectively Hispanic immigrants. I aim to decompose some of the complexity associated with endogenous identity by exploring certain personal and environmental determinants of identity. The empirical analysis in this paper documents how certain observable factors, namely personal characteristics and societal attitudes, affect the self-reported identity of Asians.

>>>>

This paper is most closely related to \textcite{hadah2024hispanicidentity, antmanEthnicAttritionObserved2016,antmanIncentivesIdentifyRacial2015,antmanAmericanIndianCasinos2021} where the authors studied the ethnic attrition of Hispanic immigrants and how minorities change their self-reported identity to changes in policies.\footnote{Ethnic attrition is when a person with Asian ancestry fails to self-identify as Asian.} Taking into consideration the ethnic attrition that \textcite{antmanEthnicAttritionObserved2016} document, I investigate the determinants of what drives a person to self-report, or not, their Asian identity. \textcite{hadah2024hispanicidentity} finds that bias and self-reported Hispanic identity are negatively associates among a sample of objectively Hispanic immigrants. I aim to decompose some of the complexity associated with endogenous identity by exploring certain personal and environmental determinants of identity. The empirical analysis in this paper documents how certain observable factors, namely personal characteristics and societal attitudes, affect the self-reported identity of Asians.
